### 2022-04-29 tesis_Rodolfo/Abstract/abstract.tex
Draft_0

\begin{abstract}
\begin{center}
    {\huge Abstract}
\end{center}
    The design and expected performance of the Tracker End-cap Pixel (TEPX) and other subdetectors as luminometers for the CMS experiment at the upcoming High-Luminosity LHC (HL-LHC) is described. The TEPX detector is composed of 4 double sided disks covering a range on $|z|$ from 175 to 265 cm, each one made of 5 rings composed of silicon sensors with a high number of pixels. Disk 4 Ring 1 (TEPXD4R1) will be designated for luminosity measurements only, utilising the same method as the TEPX luminometer, the pixel cluster counting (PCC) method. For the HL-LHC, the goal is to achieve a final uncertainty of $1\%$ for the luminosity measurements. The expected performance and linearity of the TEPX, TEPXD4R1 and other luminometers in terms of statistical precision, for van der Meer (vdM) scan calibration  and for physics conditions, are presented. The bandwidth needed for the transfer of the luminosity data and disk needed for storage are estimated.
\end{abstract}

>>>>

\begin{abstract}
\begin{center}
    {\huge Abstract}
\end{center}
    van der Meer calibration is decribed
\end{abstract}

### 2022-04-29 tesis_Rodolfo/Abstract/resumen.tex
Draft_0

\begin{abstract}
    \begin{center}
    {\huge Resumen}
\end{center}
Se describe el diseño y el rendimiento esperado del Tracker End-cap Pixel (TEPX) y otros sub detectores como luminómetros para el experimento CMS, en el próximo LHC de alta luminosidad (HL-LHC). El detector TEPX está compuesto por 4 discos de doble cara que cubren un rango en $ | z | $ de 175 a 265 cm, cada uno compuesto por 5 anillos hechos de sensores de silicio con un alto número de píxeles. El Disco 4 Anillo 1 (TEPXD4R1) se designará solo para mediciones de luminosidad, utilizando el mismo método que el luminómetro TEPX, el método de conteo de conjuntos de píxeles (PCC). Para la etapa del HL-LHC, el objetivo es lograr una incertidumbre final de $ 1 \% $ para las mediciones de luminosidad. Se presentan el rendimiento esperado y la linealidad de TEPX, TEPXD4R1 y otros luminómetros en términos de precisión estadística, para la calibración de escaneo de van der Meer (vdM) y para condiciones físicas. El ancho de banda necesario para la transferencia de los datos de luminosidad y el disco necesario para su almacenamiento es estimado.

\end{abstract}

>>>>

\begin{abstract}
    \begin{center}
    {\huge Resumen}
\end{center}
Calibracion de van der Meer
\end{abstract}

### 2022-04-29 tesis_Rodolfo/Chapter3/chapter3.tex
Draft_0

\chapter{  Luminometer system description}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Cluster coincidence algorithm }

The other object used by the TEPX luminometer to measure the event rate are two-fold coincidences. Coincidences are less prone to contamination by false hits produced in the detector after a bunch crossing (afterglow), due to the slow dissipation of charge and neutrons produced by the surrounding material (albedo). Two-fold coincidences are created when a particle hits overlapping modules, in the different layers of the TEPX disks. Due to this, coincidences are more likely to be a real hit than random electrical noise. The cylinder/disk like geometry of the TEPX detector allows for coincidences to be constructed in two ways: coincidences in $\phi$ require modules overlapping in the same ring, in front and in the back of a double sided disk, while coincidences in $r$ requires overlapping modules from different layers. These two ways of constructing two-fold coincidences are illustrated in Figure \ref{3x2x}. The surface area of overlapping modules tends to be larger in $\phi$ than in the $r$ direction. In order for a 2x coincidence to be considered, activated pixel clusters must fall in to specific cuts (on their $\delta r$ and $\delta \phi$ separations). Finally, three-fold coincidences can occur as well, however, these types of coincidences are beyond the scope of this work.\\
Coincidences provide another method of measuring luminosity and bring more stability, linearity and precision to the TEPX luminometers.
\begin{center}
\begin{figure}[H]
    \centering
    \includegraphics[scale=.4]{Chapter3/3x2x.png}
    \caption[Regions where two-fold coincidences can occur in r and $\phi$.  ]{Diagram of the regions in r and $\phi$ where pixel modules overlap, between the front and the back layers of one double-sided disk, from which two-fold coincidences come. }
    \label{3x2x}
\end{figure}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data acquisition}
After event rate measurements have been taken, the data needs to be safely transferred and stored. In order to do this, several systems are put in place. Every subdetector has a dedicated CMS subsystem or a dedicated BRIL (Beam Radiation, Instrumentation, and Luminosity) system that takes care of this process. In the case of the TEPX, and other luminometers described in section 3.4.1, a combination of CMS and BRIL systems will be used, while TEPXD4R1 will be solely operated by BRIL.\\
The way counts per bunch crossing measured by a given luminometer are stored in CMS, is by using histograms. Every time a full orbit of bunches collides (3564 bunches), the counts per bunch crossing is histogramed and stored. Depending on the geometry of the subdetector, the number of histograms generated by each changes. In the case of TEPX and TEPXD4R1 a histogram is created per quarter ring, this means that a total of 152 histograms are created by TEPX (not including the histograms from D4R1) and 8 by TEPXD4R1, in one orbit. The histograming is done by the dedicated back-end of each subdetector, a combination of software and hardware components in charge of creating these histograms. Once the histograms have been correctly created they are read, processed and stored by the BRILDAQ (BRIL data acquisition) system. Figure \ref{histhit} shows an example of a histograms for TEPX in the case of pixel clusters.
\begin{center}
    \begin{figure}[H]
        \centering
        \includegraphics[scale=0.5]{Chapter3/histbx.png}
        \caption[Histogram of the mean number of pixel clusters per bunch crossing (BX) measured by the Phase-1 pixel detector.]{The histogram shows the mean number of pixel clusters per bunch crossing (BX) for one lumisection (23.3 seconds), measured by the Phase-1 pixel detector during regular physics runs. The measurements from the 2018 data taking period.}
        \label{histhit}
    \end{figure}
\end{center}
Once histograms have been created, safely transferring and storing them is important, in order to do this the memory required to store them needs to be known. The memory size of each histogram depends on the information in each of  them. All histograms have 3564 bins, one bin for each bunch crossing, these bins store the number of counts measured in a given bunch crossing, thus, the bits of information stored in these bins will give the memory of each histogram.
\begin{equation}
    \text {Memory per Hist}= \text {No. of Bins}\times \text {bits per Bin}
    \label{histm}
\end{equation}
 where the bits per Bin are calculated using 
 \begin{equation}
     \text {bits per Bin}= log_2(N)
     \label{logn}
 \end{equation}
where $N$ is the maximum expected number of counts per bunch crossing for a given integration period, it is worth mentioning that the results from equation \ref{logn} are rounded up to the closes integer. The maximum expected number of counts per bunch crossing is given by

\begin{equation}
    N=n\frac{\text {Total Trigger Rate}}{3564}t
    \label{N}
\end{equation}
where $n$ is the mean number of counts per event and $t$ is the integration period. Equation \ref{N} assumes that the Total Trigger Rate is distributed uniformly. Once the memory of the histogram is known, the data bandwidth needed to store all the histograms can be calculated, the Data Transfer Rate is given by 
\begin{equation}
    \text {Data Transfer Rate}=\frac{No. Hist\times Memory per Hist}{t}
    \label{drate}
\end{equation}
where No. Hist is the number of histograms created by the detector and t is the time in which the information is transferred.\\

\subsection*{32-bit word implementation}
The data at CMS is not transferred bit by bit, rather, is transferred in packages of information called words. Each word contains 32-bits of information, this means that all data transferred has to, first, be converted in to a 32-bit word. The way this is applied to the histograms is by converting the information in each bin in to a word, this is done in two ways:
\begin{itemize}
    \item If the Bits per bin$\leq16$ bits, the number of bits is
rounded to 16 and two bins are grouped in one word.
\item If $16\leq$ Bits per bin$\leq32$,  the number of bits is
rounded to 32-bit word and one word is used for each bin.
\end{itemize}

Aside from this, the TEPX luminometers use additional words for the overhead of the histograms data format:
\begin{itemize}
    \item 9 words for the header for TEPX and D4R1.
    \item  768 words for errors for TEPX and 160 for D4R1.
    \item 4 words for the mask for TEPX and 2 forD4R1.
\end{itemize}
These additional data has to be taken in to account for each histograms, when calculating the needed memory to store and transfer them. Finally, using equation \ref{logn} the bits per bin can be calculated, using data from the high pileup simulation \cite{datarates}. The results for the TEPX luminometers is shown in Table \ref{bitsperbin}.
\begin{table}[ht]
\centering
\caption[ Memory bits required per histogram bin for the TEPX luminometers.]{Table shows the Trigger rate (kHz), counts per event per detector unit (histogram), number of counts per bx per integration period (1s) and the memory bits required per histogram bin.}
\scalebox{.7}{
\begin{tabular}{|l |c |c |c |c|}
\hline
&  Trigger rate (kHz) & Counts per event & Counts/bx/1s&Bits/bin\\
\hline
TEPXD4R1 Clusters&825&539&1.25e+05&17\\
\hline
TEPXD4R1 2x Coincidences&825&54&1.25e+04&14\\
\hline
TEPX Clusters&75&539&1.13e+04&14\\
\hline
TEPX 2x Coincidences&75&54&1.14e+03&11\\
\hline
\end{tabular}}
\label{bitsperbin}
\end{table}
Using this and equation \ref{drate}, the data rates can be calculated, the results are shown in Table \ref{dataratet} for a transferring time of 1 s.
\begin{table}[ht]
\centering
\caption[Data transfer rates for the TEPX luminometers.]{Data transfer rates for the TEPX luminometers for pileup 200. Columns shown are number of histograms, memory per histogram and data transfer rates (Mbps) for an integration period of 1s. }
\scalebox{.8}{

\begin{tabular}{|l  |c |c |c|}
\hline
&  Number of Histograms & Memory per histogram (Kb) & Data Transfer Rates (Mbps)\\
\hline
TEPXD4R1 Clusters&8&124&0.95\\
\hline
TEPXD4R1 2x Coincidences&8&67&0.5\\
\hline
TEPX Clusters&152&82&12.5\\
\hline
TEPX 2x Coincidences&152&82&12.5\\
\hline
\end{tabular}}
\label{dataratet}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Other luminometers}

The TEPX luminometer is not the only luminometer of the CMS Phase-2 detector, each layer of the detector will have a dedicated luminometer, and corresponding algorithm, to ensure the best luminosity measurements possible.
Figure \ref{cmslum} shows the location of the different luminometers at the CMS detector, for the Phase-2 upgrade. A brief description of the luminometers is presented below.
\begin{center}
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.3]{Chapter3/cmdlum.png}
    \caption[Different subsystems and luminometrs at CMS.]{Layout of the different subsystems and luminometrs at CMS. }
    \label{cmslum}
\end{figure}
\end{center}
\subsection*{Outer tracker layer 6}
From the outer tracker (OT), layer 6 will be a designated luminometer. The object used by these luminometer are track stubs, which are two-hit coincidences between closely spaced silicon modules. Figure \ref{ot} show the layout of the new Phase-2 outer tracker, layer 6 is located in the outer tracker barrel, specifically, the TB2S section.
\begin{center}
\begin{figure}[H]
    \centering
    \includegraphics[scale=.4]{Chapter3/ot.png}
    \caption[Outter tracker layout.]{Diagram of the different parts that conform the outer tracker, the two barrel regions, TBPS and TB2S, and the end-cap region TEDD. The OT layer 6 luminometer corresponds to the last upper layer of TB2S. }
    \label{ot}
\end{figure}
\end{center}

Layer 6 consists of 76 ladders of 12 strip modules made of two Si-strip sensors, as shown in Figure \ref{otlather} (left). The ladders span fully, in the azimuthal range, at each end of the CMS detector. The reconstruction method of the track stubs is shown in Figure \ref{otlather} (right) as well. The tracks are reconstructed at 40 MHz.
\begin{center}
\begin{figure}[H]
    \centering
    \includegraphics[scale=.7]{Chapter3/otlather.PNG}
    \caption[Example of an OT layer 6 ladder and the stub selection process.]{\textit{Left}: An example of a ladder with the the 12 strip modules (regions in yellow). \textit{Right}: Diagram of the stub selection process. The black squares represent hits, and the green squares represent the regions where the other hit could take place, to be considered a stub.}
    \label{otlather}
\end{figure}
\end{center}

The OT layer 6 luminometers, creates one histograms per one 12 module ladder, for a total of 152. As well as the TEPX luminometers, the histograms created in layer 6 will have additional words for the overhead of the histograms data format:
\begin{itemize}
    \item 9 words for the header.
    \item  192 words for errors.
    \item 4 words for the mask.
\end{itemize}

Figure \ref{otstubs} shows the expected number of track stubs per bunch crossing as function of the ladders ID. Tables 3.3
and 3.4 show the expected Bits per Bin and the Data Transfer Rates for the OT layer 6 luminometer, calculated using data from the high pileup simulation.
\begin{center}
\begin{figure}[H]
    \centering
    \includegraphics[scale=.4]{Chapter3/OT-Rates.png}
    \caption[Simulated expected number of stubs per ladder per event.]{Simulated expected number of stubs per ladder per event as a function of ladder ID.}
    \label{otstubs}
\end{figure}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Muon drift tube}
The muon DT luminometer follows the same design described in section 2.2. The entire DT system is formed by 250 gas chambers, installed in the barrel yoke of the CMS detector, as shown in Figure \ref{Muons}. The chambers are distributed across 5 wheels labeled YB0, YB$\pm1$ and YB$\pm2$, four radial stations, MB1-MB4, and 12 $\phi$ sectors \cite{ABBIENDI2009192}.

The objects used by this luminometer are called trigger primitives, which are reconstructed muon track segments per DT chamber. The tracks are reconstructed at a trigger frequency of  40 $MHz$,  using hits from the DT and RPC detectors. The rate of trigger primitives has being studied and extrapolated to the expected  instantaneous luminosity of the HL-LHC, $7.5\times 10^{34}$ $cm^{-2}s^{-1}$, using  the data from Run 2. Figure \ref{dtrate} shows the expected rates for the YB0 and YB+2 wheels. The large difference on the measured rate, between the MB1 and the rest of the chambers in the MB2 and MB3 stations, is due to a significant contribution of particle from punch-through jets.
\begin{figure}[H]
\centering
\includegraphics[width=.48\textwidth]{Chapter3/DT_Trigger_extraploation_YB.pdf}
\includegraphics[width=.48\textwidth]{Chapter3/DT_Trigger_extraploation_YBp2.pdf}
\caption[Expected rates of trigger primitives per DT chamber]{Expected rates of trigger primitives per DT chamber for the YB0 (left) and YB+2 (right) wheels.}
\label{dtrate}
\end{figure}
The DT luminometer will create one histogram per DT chamber, giving a total of 250 histograms. Tables \ref{bitsperbinall} and \ref{dataratesall} show the expected Bits per Bin and the  Data Transfer Rates for the DT luminometer, using extrapolated data from the 2018 data taking period.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{BMTF }
The Barrel Muon Track Finder (BMTF) is an algorithm that uses reconstructed muon tracks to provide luminosity measurements. As its name suggests, The algorithm uses information from all the DT and RPC gas chambers, located in the barrel of the muon system, to reconstruct muon tracks.
One histograms is created by the algorithm. Tables \ref{bitsperbinall} and \ref{dataratesall} show the expected Bits per Bin and the  Data Transfer Rates for the BMTF algorithm \cite{Bachtis:2648953}. As well as the DT luminometer, BTMS uses  extrapolated data from the 2018 data taking period.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Data transfer rates for all luminometers}
Using the number of histograms, as well as the mean number of counts per event for each luminometer \cite{datarates}, the number of Bits per Bin as well as the Data Transfer Rates can be calculated for all luminometers. This is shown is Tables \ref{bitsperbinall} and \ref{dataratesall} respectively.
\begin{table}[H]
\centering
\caption[Memory bits required per histogram bin for all luminometers.]{Triger rate (kHz), counts per event per detector unit (histogram), number of counts per bx per integration period (1s) and the memory bits required per histogram bin.}
\scalebox{.7}{
\begin{tabular}{|l |c |c |c |c|}
\hline
&  Trigger rate (kHz) & Counts per event & Counts/bx/1s&Bits/bin\\
\hline
TEPXD4R1 Clusters&825&539&1.25e+05&17\\
\hline
TEPXD4R1 2x Coincidences&825&54&1.25e+04&14\\
\hline
TEPX Clusters&75&539&1.13e+04&14\\
\hline
TEPX 2x Coincidences&75&54&1.14e+03&11\\
\hline
OT Layer 6 track stubs&40000&8&8.98e+04&17\\
\hline
DT Trigger Primitives&40000&0.0125&140&8\\
\hline
BMTF Tracks&40000&0.041&460&9\\
\hline
\end{tabular}}
\label{bitsperbinall}
\end{table}
\begin{table}[H]
\centering
\caption[Data transfer rates for the different luminometers.]{Data transfer rates for the different luminometers for pileup 200. Columns shown are number of histograms, memory per histogram and data transfer rates (Mbps) for an integration period of 1s. }
\scalebox{.8}{
\begin{tabular}{|l  |c |c |c|}
\hline
&  Number of Histograms & Memory per histogram (Kb) & Data Transfer Rates (Mbps)\\
\hline
TEPXD4R1 Clusters&8&124&0.95\\
\hline
TEPXD4R1 2x Coincidences&8&67&0.5\\
\hline
TEPX Clusters&152&82&12.5\\
\hline
TEPX 2x Coincidences&152&82&12.5\\
\hline
OT Layer 6 track stubs&152&120&18.3\\
\hline
DT Trigger Primitives&250&28&7.13\\
\hline
BMTF Track&1&57&0.057\\
\hline
\end{tabular}}
\label{dataratesall}
\end{table}

From these tables it can be concluded that the minimum bandwidth required will be 18.3 Mbps, corresponding to the OT luminometer. The total storage needed per day for all luminometers presented here can be calculated, assuming an operation time of 12 hours, the total storage needed will be 280.46 GB. Since other luminometers will be in operation, besides the ones discussed here, 280.46 GB is the minimum storage per day required to ensure no data is lost.

>>>>

\chapter{ Luminometer system and calibration description}

%%%%Introduction%%%%%%%%%%%%%%%%%%%%5

A total of seven systems are used for measuring luminosity at CMS, being the PCC one of them.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{2018 Calibration Scan program}
The VdM scans, and other scans regarding to calibrations, were performed during the LHC fill 6868 on June 30 and July 1, 2018 at $\sqrt{s}=13TeV$. The LHC filling scheme used 124 colliding bunch pairs at the CMS interaction point (IP5) widely spread over the orbit to reduce long range beam-beam effects and detector afterglow. The resulting beam size $\sigma_{b}$ at the beginning of the fill was in the range of approximately 85–95 and 80–90 $\mu m$ in $x$ and $y$, respectively, increasing over time in the $x$ dimension and decreasing over time in the $y$ dimension.No crossing angle was used for collisions at ATLAS and CMS. The resulting peak pileup was approximately $\mu = 0.6$ , much lower than in a regular physics fill.

The bunch intensities were approximately $7-9 \times 10^{10} $ protons per filled bunch, resulting in a total beam intensity of slightly above $10^{13}$ protons per beam. The total beam intensities were measured with the DC Current Transformers (DCCT) [15], and the bunch currents were measured with the Fast Beam Current Transformers (FBCT) [16]. The beam orbit was monitored using two systems, the DOROS beam position monitors (BPMs) [17] located near IP5, and the arcBPMs located in the LHC arcs adjacent to CMS.  ***The orbit is also tracked using movements of the luminous region based on reconstructed vertices. The arc BPM measurements are translated to a beam position at IP5 using the LHC optics file; the specific optics file used for this scan is R2016c A19mC19mA19mL24.

To ensure a dataset with a high event count for PCC even at large beam separations, CMS recorded the zero-bias triggers on 5 bunch pairs (BCIDs 265, 865, 1780, 2192, and 3380) and recorded events with a total rate of $27.7kHz$.

The CMS VdM scan program was conducted in two parts (``takes''), due to an alarm. The first part consisted of a total of six x-y scan pairs. Two (``emit1'' and ``emit'') were short ``emittance'' scans, in which the two beams were separated by $4sigma_{b}$ in 9 steps with 10 seconds integration time at each scan point.***
Scan pair ``norm1'' was a standard VdM scan, in which the two beams were separated by $6\sigma_{b} \approx 600 \mu m$  and scanned across one another in a sequence of 25 steps with 30 seconds per step.

The second part of the scan program was conducted in the same fill but about $7.5$ hours later. It consisted of twelve scan pairs. Scan pair ``emit3'' was a short emittance scan, followed by scan pairs ``imag2'' and ``imag3'' of the beam imaging kind, an offset scan pair ``offset2'', and finally two normal VdM scan pairs ``norm2'' and ``norm3''. The latter two allow us to test the reproducibility of the measuremen.

****After ``norm3'' scan pair, there were the first superseparation period, in which the beams are separated a distance of $6 \sigma_{b}$ in both $x$ and $y1 direction$ for $5$ minutes long in order to get a bakcground estimation.**** source: Analyis Note 2018

A length scale calibration (LSC) was performed after scan pair ``norm3'' using two different methods. The first, ``lsc1'', was the ``constant separation'' scan, in which the two beams were separated by $1.4\sigma_{b}$ (approximately equal to $1\Sigma$) and moved together in steps of $1\sigma_{b}$ across and back, for a total of $10$ steps with $70$ seconds per step, once in each transverse direction. A second ``variable separation'' method with scan pair ``lsc2'' was also executed, in which one beam (starting with beam 1) is moved to $-2.5\sigma_{b}$ and then a three-point scan (a ``miniscan'') is performed with the other beam (starting with beam 2) at a relative position of $-1.25\sigma_{b}$, $0$, and $+ 1.25 \sigma_{b}$. The position of the first beam is then translated in five steps in the same direction to $+2.5 \sigma_{b}$, repeating the miniscan at each step. This procedure is repeated four times, with two directions for each of the two beams. Each scan point has a duration of about $46s$.

Finally, a normal VdM scan pair “norm4”,*** a second super separation period***,  and two short emittance scan pairs “emit4” and“emit5” concluded the program.

In each scan pair, the scan was performed first in the x direction and then in the y direction, with the exception of the variable separation length scale calibration scan pairs, which were done the other way around.
Figure \ref{2018sp} shows the beam positions for the two beams in the x and y directions as measured by the DOROS BPMs during the scan program, showing all 18 scan pairs.
\begin{center}
    \begin{figure}[H]
        \centering
        \includegraphics[scale=0.5]{Chapter3/2018Scanprogram.png}
        \caption[2018 San program.]{Relative change in beam positions measured by the DOROS BPMs during the 2018 scan program for the two individual beams in the horizontal x and vertical y planes, as a function of the elapsed time from the beginning of the program. The top row shows the portion ofthe scan program before the alarm at CMS, while the bottom two rows show the scan program after the alarm.[source: pas-lum-18]}
        \label{2018sp}
    \end{figure}
\end{center}

The beam imaging and offset scans are intended for specific studies on the beam shapes described in Section 4**, and they can also be analyzed as traditional van der Meer scans. Both the LSC and beam imaging scans are discussed in detail in Ref. [18**]. The offset scan data is analyzed for the first time in 2018.

source: pas-lum-18
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Corrections and systematic uncertainties}
There are several systematic effects which affect the beam overlap width measurement, and hence the $\sigma_{vis}$ is extracted from the VdM scan procedure. These effects are measured and, where applicable, corrected as described below, and a systematic uncertainty is assigned to the resulting measured cross section for each source.

Framework correction flags

\begin{itemize}
 \item ghost and satellite
 \item Background (several types, in our case from SS)
 \item Orbit drift (sep and rate)
 \item Beam Beam
 \item DynamicBeta
 \item Length Scale
 \item PeakToPeak
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Beam beam correction}
Beam beam correction:

\subsection{Veto module correction?}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
